Molecular Gas Kinematics of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-11-22 WRITEUP/ms.tex
the source file for ms.pdf in bf07670 (2 commits before), forgot to add this together in that commit

\begin{figure}[!htbp]
%\centering
\includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
\caption{CARMA \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
The velocity scale is the same as in \Fig{CO21spec}
The spectral resolution for \cco and \bco
is 36 \kms and 22 \kms, respectively.
 \label{fig:co32spec}}
\end{figure}

@@

We detect 2.2\,mm continuum emission at an
 integrated flux density of
1.2\pmm0.2 mJy, with a peak flux of
$S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
centered on the lensing galaxy (\Fig{cont}).
% We note that the reported flux uncertainties do not include those from absolute flux calibration.
Slightly extended emission
along the lensed arc is also detected.
This suggests that we detect emission in both
the foreground and background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in the $uv$-plane to remove the unresolved part of the
emission, which we here assume to be dominated by the foreground galaxy. The peak emission
in the residual map coincides with the lensed arc, with a flux density 
of $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy. 
This peak flux is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). 
We therefore adopt $S_{\nu}$\eq0.39\pmm0.12 mJy as the 2\,mm continuum flux measurement for 
the background galaxy (RXJ1131). 
The quoted uncertainty is derived by adding those associated with the flux density of the 
point-source model ($\delta S_{\nu}$\eq0.088\,mJy) and 
the peak flux in the residual map (0.08\,mJy) 
in quadrature, and does not account for that in the 
de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
We report the peak flux in the original map
($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy, which
is the best estimate possible at the resolution of our observations, but we acknowledge that a non-negligible contribution from the background source to the peak flux cannot be ruled out.

>>>>

\begin{figure}[!htbp]
%\centering
\includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
\caption{CARMA \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
The velocity scale is the same as in \Fig{CO21spec}.
The spectral resolution for \cco and \bco
is 36 \kms and 22 \kms, respectively.
 \label{fig:co32spec}}
\end{figure}

@@

We detect 2.2\,mm continuum emission at an
 integrated flux density of
1.2\pmm0.2 mJy, with a peak flux of
$S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
centered on the lensing galaxy (\Fig{cont}).
% We note that the reported flux uncertainties do not include those from absolute flux calibration.
Slightly extended emission
along the lensed arc is also detected.
This suggests that we detect emission in both
the foreground and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in the $uv$-plane to remove the unresolved part of the
emission, which we here assume to be dominated by the foreground galaxy. The peak emission
in the residual map coincides with the lensed arc, with a flux density 
of $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy. 
This peak flux is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). 
We therefore adopt $S_{\nu}$\eq0.39\pmm0.12 mJy as the 2\,mm continuum flux measurement for 
the background galaxy (RXJ1131). 
The quoted uncertainty is derived by adding those associated with the flux density of the 
point-source model ($\delta S_{\nu}$\eq0.088\,mJy) and 
the peak flux in the residual map (0.08\,mJy) 
in quadrature, and does not account for that in the 
de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
We report the peak flux in the original map
($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy, which
is the best estimate possible at the resolution of our observations, but we acknowledge that a non-negligible contribution from the background source to the peak flux cannot be ruled out.
